\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Muhammad Fakhruddin Fu'ad} \\
  \href{tel:+6285900228435}{6285900228435} $|$ 
  \href{mailto:fakhruddinfuad29@gmail.com}{fakhruddinfuad29@gmail.com} $|$ 
  \href{https://www.linkedin.com/in/muhammad-fakhruddin-fu-ad-b6850b23b/}{linkedin.com/in/muhammad-fakhruddin-fu-ad-b6850b23b/}
\end{center}

\section*{Summary}
I am a person with enthusiasm and professional experience in the IT field as a Fullstack Web Developer for 8 months and 4 months as an IT Project Manager. I have developed various web applications that are not only functional but also efficient and user-friendly, both for independent and corporate projects. With expertise in Laravel, I am adept at managing the entire application development cycle, from back-end to front-end. As an IT Project Manager, I lead the team to complete projects on time with high quality standards, integrate modern technology, and implement best practices in project management.

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: HTML, CSS, Javascript, PHP, MySQL, PostgreSQL}
  \resumeItem{\textbf{Libraries \& Tools}: Laravel, jQuery, Bootstrap, yajra DataTables, Git \& GitHub, Postman, Composer}
  \resumeItem{\textbf{Hardskills}: Web Development, Database Management, RESTful API, Version Control, Debugging, Agile Method, Project Management}
  \resumeItem{\textbf{Softskills}: Leadership, Problem Solving, Collaboration, Analytical Thinking, Time Management, Adaptability, Communication}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {IT Project Manager}{Sept 2024 -- Jan 2025}
      {Kawan Kerja}{Bandung, ID} \\
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Lead and manage IT projects from start to finish, including planning, organizing and controlling all aspects of the project.}
          \resumeItem{\textbullet\ Determine the project scope, objectives, and budget, and develop detailed plans to achieve set targets.}
          \resumeItem{\textbullet\ Manage cross-functional project teams, including developers, analysts, designers, and testers, and allocate resources to maximize efficiency.}
          \resumeItem{\textbullet\ Communicate regularly with internal and external stakeholders to report on project progress, obstacles encountered, and milestones achieved.}
          \resumeItem{\textbullet\ Identify and manage project risks, and develop mitigation strategies to ensure smooth project implementation.}
          \resumeItem{\textbullet\ Prepare complete project documentation, including progress reports, schedules, and ensure projects are completed on time and within budget.}
          \resumeItem{\textbullet\ Ensure all deliverables comply with established quality standards and meet client requirements.}
          \resumeItem{\textbullet\ Apply Agile and Scrum methodologies to all projects, increasing delivery speed and team collaboration.}
          \resumeItem{\textbullet\ Leading and managing 9 IT projects simultaneously, from planning, implementation, to completion. These include the ENGLISH, RAMADHAN, KALKULATOR ZAKAT, KAWAN QUR'AN, KAWAN BAYAR, TA'ARUF ONLINE, SAPA, BARCHERRY, and MUHAMMAD projects}
      \resumeSubHeadingListEnd
      
  \resumeSubheading
      {Fullstack Developer}{Sept 2024 -- Dec 2024}
      {PT Citra Gama Sakti}{Yogyakarta, ID} \\
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developing various application projects such as Human Resources Information Systems, mini e-commerce, and mini blogs using the Laravel framework}
          \resumeItem{\textbullet\ Implemented several modules and packages such as domPDF, maatweb excel, Breeze, Spatie, Yajra Datatables, etc. to support the project development process}
          \resumeItem{\textbullet\ Work collaboratively within a development team to plan, design, and implement software solutions that meet client needs and industry standards.}
          \resumeItem{\textbullet\ Responsible for application testing, ensuring functionality goes as planned, and resolving bugs or technical issues as they arise.}
          \resumeItem{\textbullet\ Implement good coding practices with version control using Git and work efficiently using SCRUM methodology.}
          \resumeItem{\textbullet\ Deployment applications to hosting servers using cPanel, SSH or FTP and ensure optimal and secure performance.}
          \resumeItem{\textbullet\ Lead and manage IT projects from start to finish, including planning, organizing and controlling all aspects of the project.}
      \resumeSubHeadingListEnd
      \vspace{0.4in}
  \resumeSubheading
      {Fullstack Web Developer}{Aug 2023 -- Dec 2023}
      {PT Mitra Bestari Teknologi}{Bandung, ID} \\
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developing a website-based KLIKMEDIS application project using the Laravel framework}
          \resumeItem{\textbullet\ Implemented several modules and packages such as domPDF, maatweb excel, Breeze, Spatie, Yajra Datatables, etc. to support the project development process}
          \resumeItem{\textbullet\ Work together with the team in developing and implementing application features according to the needs and tasks given by the project leader}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

% \section{Projects}
% \resumeSubHeadingList
%   \resumeSubheading
%       {Image Captioning System}{Jan 2023 -- Present}
%       {Deep Learning Project}{Python, TensorFlow, OpenCV}
%       \resumeSubHeadingList
%           \resumeItem{\textbullet\ Developed an end-to-end system for generating descriptive captions for images}
%           \resumeItem{\textbullet\ Utilized CNN and LSTM models for image feature extraction and caption generation}
%           \resumeItem{\textbullet\ Achieved state-of-the-art performance on the COCO dataset}
%       \resumeSubHeadingListEnd
%   \resumeSubheading
%       {Sentiment Analysis API}{Aug 2022 -- Dec 2022} 
%       {Natural Language Processing}{Python, Flask, NLTK, Hugging Face}
%       \resumeSubHeadingList
%           \resumeItem{\textbullet\ Built a RESTful API for sentiment analysis of text data}
%           \resumeItem{\textbullet\ Implemented pre-trained transformer models using Hugging Face}
%           \resumeItem{\textbullet\ Deployed the API on a cloud platform for easy integration}
%       \resumeSubHeadingListEnd
% \resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Universitas Wahid Hasyim}{Semarang, ID}
      {Informatics Engineering}{Sept 2021 -- Present}
  \resumeSubheading
      {MA Taqwal Ilah}{Semarang, ID}
      {Social Science}{Jun 2018 -- Jun 2021}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\textbullet\ \href{https://drive.google.com/file/d/1I5-TYqm2pZG1axxwgvooE3N1Yt7ndzix/view?usp=sharing}{Fullstack Developer - PT Citra Gama Sakti}}
  \resumeItem{\textbullet\ \href{https://drive.google.com/file/d/1gXP7IY-nlXnFLyBVYMxH2hvolo24P5uf/view?usp=sharing}{Fullstack Developer - Kampus Merdeka MSIB 7}}
  \resumeItem{\textbullet\ \href{https://drive.google.com/file/d/1w7MXQxv3cCrubTDo4msD4kQ5zSHkZ2Nk/view?usp=sharing}{Dasar Framework Laravel - Bisa AI}}
  \resumeItem{\textbullet\ \href{https://drive.google.com/file/d/1ofTP_1304GDRNLfoTA9biHpumaGSnjNE/view?usp=sharing}{Junior Web Developer - PT Mitra Bestari Teknologi}}
  \resumeItem{\textbullet\ \href{https://www.dicoding.com/certificates/RVZKR0L1QPD5}{Membuat Aplikasi Back-End Pemula - Dicoding}}
  \resumeItem{\textbullet\ \href{https://www.dicoding.com/certificates/72ZDVK636ZYW}{Cloud Practitioner Essentials (Belajar Dasar AWS Cloud) - Dicoding}}
  \resumeItem{\textbullet\ \href{https://www.dicoding.com/certificates/1OP8W4QK1XQK}{Dasar AI - Dicoding}}
  \resumeItem{\textbullet\ \href{https://www.dicoding.com/certificates/RVZKREDYMPD5}{Dasar Structured Query Language (SQL) - Dicoding}}
\resumeSubHeadingListEnd

\end{document}